---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# cividis

[![Build Status](https://travis-ci.org/marcosci/cividis.svg?branch=master)](https://travis-ci.org/marcosci/cividis)
[![codecov](https://codecov.io/gh/marcosci/cividis/branch/master/graph/badge.svg)](https://codecov.io/gh/marcosci/cividis)

Jamie R. Nuñez, Christopher R. Anderton, and Ryan S. Renslow recently
[introduced optimized color maps](https://arxiv.org/ftp/arxiv/papers/1712/1712.01662.pdf)
for the scientific community. This so-called "cividis" colormap is generated
by optimizing the ["viridis" colormap](https://bids.github.io/colormap/) and is
optimal for viewing by those with or without color vision deficiency (CVD), a
different visual perception of colors that affects 8.5% of the human population.
It is designed to be perfectly perceptually-uniform, both in regular form and
also when converted to black-and-white, and can be perceived by readers with
all forms of color blindness. The cividis colormap was developed as a
[Python module called "cmaputil"](https://github.com/pnnl/cmaputil).

Because of the high interest of the scientific community in R, we make this
new colormap available as an R package!

This is how the colormap looks like in comparison to viridis colors and from the view of a blue-blind person:


```{r  echo=FALSE, message=FALSE, fig.height=2.86}
n_col <- 128

img <- function(obj, nam) {
  image(1:length(obj), 1, as.matrix(1:length(obj)), col=obj, 
        main = nam, ylab = "", xaxt = "n", yaxt = "n",  bty = "n")
}

library(viridis)
library(scales)
library(colorspace)
library(dichromat)

par(mfrow=c(5, 1), mar=rep(1, 4))
img(rev(cividis(n_col)), "cividis")
img(rep("#FFFFFF", 128), nam = "")
img(rev(viridis(n_col)), "viridis")
img(rev(magma(n_col)), "magma")
img(dichromat(rev(cividis(n_col)), "tritan"), "cividis blue-blind (tritanopia)")
```

... and like this in action (coloring neutral landscape models from [NLMR](https://github.com/marcosci/NLMR)): 

```{r echo=FALSE, message=FALSE, fig.height=15, fig.width=7, fig.align='center'}
library(NLMR)
library(rasterVis)
library(ggplot2)
library(patchwork)
library(cividis)

# simulate NLM
x <- nlm_random(ncol = 100,
                nrow = 100)

x1 <- nlm_gaussianfield(ncol = 100,
                        nrow = 100,
                        autocorr_range = 30)

x2 <- nlm_mosaicfield(ncol = 100,
                      nrow = 100,
                      n = 30)

x3 <- nlm_curds(c(0.9, 0.6, 0.6), c(20, 10, 5))


gplot(x) +
 geom_tile(aes(fill = value)) +
 labs(x = "Easting",
      y = "Northing") +
 theme_nlm() +
 scale_fill_cividis(
    na.value = "transparent",
    name = "",
    guide = ggplot2::guide_colorbar(
      barheight = ggplot2::unit(40, units = "mm"),
      barwidth = ggplot2::unit(1, units = "mm"),
      draw.ulim = FALSE,
      title.hjust = 0.5,
      title.vjust = 1.5,
      label.hjust = 0.5
 )) -> p1


gplot(x1) +
 geom_tile(aes(fill = value)) +
 labs(x = "Easting",
      y = "Northing") +
 theme_nlm() +
 scale_fill_cividis(
    na.value = "transparent",
    name = "",
    guide = ggplot2::guide_colorbar(
      barheight = ggplot2::unit(40, units = "mm"),
      barwidth = ggplot2::unit(1, units = "mm"),
      draw.ulim = FALSE,
      title.hjust = 0.5,
      title.vjust = 1.5,
      label.hjust = 0.5
 )) -> p2


gplot(x2) +
 geom_tile(aes(fill = value)) +
 labs(x = "Easting",
      y = "Northing") +
 theme_nlm() +
 scale_fill_cividis(
    na.value = "transparent",
    name = "",
    guide = ggplot2::guide_colorbar(
      barheight = ggplot2::unit(40, units = "mm"),
      barwidth = ggplot2::unit(1, units = "mm"),
      draw.ulim = FALSE,
      title.hjust = 0.5,
      title.vjust = 1.5,
      label.hjust = 0.5
 )) -> p3


gplot(x3) +
 geom_tile(aes(fill = value)) +
 labs(x = "Easting",
      y = "Northing") +
 theme_nlm_discrete() +
 scale_fill_cividis(
    discrete = FALSE,
    na.value = "transparent",
    name = "",
    guide = ggplot2::guide_colorbar(
      barheight = ggplot2::unit(40, units = "mm"),
      barwidth = ggplot2::unit(1, units = "mm"),
      draw.ulim = FALSE,
      title.hjust = 0.5,
      title.vjust = 1.5,
      label.hjust = 0.5
 )) -> p4

p1 + p2 + p3 + p4 + plot_layout(ncol = 1)
```

## Installation

To install the developmental version of ``cividis``, use the following R code:

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("marcosci/cividis")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code

# load packages
library(NLMR)
library(rasterVis)
library(cividis)

# simulate NLM
x <- nlm_random(ncol = 100,
                nrow = 100)

# plot it
gplot(x) +
 geom_tile(aes(fill = value)) +
 labs(x = "Easting",
      y = "Northing") +
 theme_nlm() +
 scale_fill_cividis(
    na.value = "transparent",
    name = "",
    guide = ggplot2::guide_colorbar(
      barheight = ggplot2::unit(40, units = "mm"),
      barwidth = ggplot2::unit(1, units = "mm"),
      draw.ulim = FALSE,
      title.hjust = 0.5,
      title.vjust = 1.5,
      label.hjust = 0.5
 )) -> p1
```

## Maintainer(s)

Marco Sciaini - [@msciain](https://twitter.com/msciain) - <sciaini.marco@gmail.com>

## Author(s)

Marco Sciaini - [@msciain](https://twitter.com/msciain) - <sciaini.marco@gmail.com>   
Cédric Scherer - [@CedScherer](https://twitter.com/CedScherer) - <cedricphilippscherer@gmail.com>

## References

The colormap in the `cividis` package was
[created](https://github.com/pnnl/cmaputil) and
[published](https://arxiv.org/ftp/arxiv/papers/1712/1712.01662.pdf) by Jamie
R. Nuñez ([@jamienunez](https://github.com/jamienunez)) and colleagues.

The package is mainly a cheeky copy of the beautiful
[`viridis` package for R](https://github.com/sjmgarnier/viridis) that was
created by [Simon Garnier](https://twitter.com/sjmgarnier),
[Noam Ross](https://twitter.com/noamross), and
[Bob Rudis](https://twitter.com/hrbrmstr).
